\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-03 paper/ms.tex
Changed plot, more writing

\citet{rjobject} described the motivation for \code{RJObject} and some details
about the Metropolis proposals underlying it. Here, we demonstrate how to
implement a finite mixture model using \code{RJObject}.
This example can be found in the
\begin{center}
{\tt code/Examples/RJObject\_1DMixture}
\end{center}
directory.

@@

Making the connection with Equation~\ref{eqn:rjobject} and
Figure~\ref{fig:rjobject_pgm}, the ``components'' are the gaussians,
the gaussian parameters are $x_j = \{\mu_j, \sigma_j, w_j\}$
and hyperparameters $\alpha$ may be used to help specify
a sensible joint prior for the gaussian parameters.
To implement this model for \pkg{DNest4}, the model
class only needs to contain an instance of an
\code{RJObject}, like so:

@@

To help with implementing the member functions for the \code{MyModel} class,
the \code{gaussians} object can be generated from its prior, proposed,
and printed trivially as follows:
\begin{CodeInput}
\begin{CodeChunk}
    // Generate the components from the prior
    gaussians.from_prior(rng);

@@

    // Print to output stream 'out'
    gaussians.print(out);
\end{CodeChunk}
\end{CodeInput}

>>>>

\citet{rjobject} described the motivation for \code{RJObject} and some details
about the Metropolis proposals underlying it. Here, we demonstrate how to
implement a finite mixture model using \code{RJObject}.
This example can be found in the
{\tt code/Examples/RJObject\_1DMixture}
directory. The ``SineWave'' and ``GalaxyField'' models
from \citet{rjobject} are also included in the \pkg{DNest4} repository.

@@

Making the connection with Equation~\ref{eqn:rjobject} and
Figure~\ref{fig:rjobject_pgm}, the ``components'' are the gaussians,
the gaussian parameters are $\{x_j\} = \{(\mu_j, \sigma_j, w_j)\}$,
and hyperparameters $\alpha$ may be used to help specify
a sensible joint prior for the gaussian parameters.
To implement this model for \pkg{DNest4}, the model
class only needs to contain an instance of an
\code{RJObject}, like so:

@@

To help with implementing the member functions for the \code{MyModel} class,
the \code{gaussians} object can be generated from its prior, proposed,
and printed trivially as follows:
\begin{CodeChunk}
\begin{CodeInput}
    // Generate the components from the prior
    gaussians.from_prior(rng);

@@

    // Print to output stream 'out'
    gaussians.print(out);
\end{CodeInput}
\end{CodeChunk}

The \code{RJObject} constructor definition is:
\begin{CodeChunk}
\begin{CodeInput}
RJObject(int num_dimensions, int max_num_components, bool fixed,
         const ConditionalPrior& conditional_prior,
         PriorType prior_type=PriorType::uniform);
\end{CodeInput}
\end{CodeChunk}
